Manuscript_Github_Pchabaudi_pir

### 2021-03-22 Manuscript_pirAnalysis_Github/Pchabaudi24h/Manuscript_Github_Pchabaudi_pir.Rmd
Phaseograms only RMT

                       if(use_times){
                         colnames(heatmap_data) <- times_stages_table$time[match(colnames(heatmap_data),
                                                                                 times_stages_table$r_stage_diff_count)]
                       }

@@

draw_heatmap_zscore(zscore_list = twentyfour_z,
                    gene_ordering_vector = phaseogram_time_order$SBP$zscore_order$Geneid,
                    filter_genes_vector = cir_id,
                    annotation_clade = 'SorL',
                    annotation_col = SorL_col,
                    threshold_tpm = 1,
                    use_times = TRUE,
                    use_order_vector = FALSE,
                    show_row_names = FALSE,
                    tpm_breaks = tpm_breaks,
                    tpm_mat = FALSE)

>>>>

                       if(use_times){
                         colnames(heatmap_data) <- str_extract(colnames(heatmap_data), 
                                                               pattern = '[[:digit:]]{2}h')
                       }

@@
